---
format: 
  html:
    theme: RLadies-styles.scss
    toc: true
    toc-location: left
    toc-depth: 3
    smooth-scroll: true
---

## {{< fa code-merge title="merging code into main" >}} Redeploy your website changes {#redeploy}

We've made lots of great changes, and now we need to publish them. Thankfully, this is fairly straightforward:

1. **Render your website.** You can do this by either navigating to the **Build** tab in RStudio and clicking the **Render Website** button, *or* running `render quarto` in your Terminal. This converts all `.qmd` files to `.html` and ensures that all website components are stitched together correctly. If you do not render your website before pushing your files, your changes will not deploy.

2. **Push your files to GitHub.** You can do so using the RStudio GUI buttons in the **Git** tab or via the Terminal. 

3. **Voila! Keep an eye on the GitHub Actions tab** to see when your redeployed website is ready to view.

::: {.callout-tip collapse="true"}
## Working on branches is recommended!

Despite not practicing it here today, I almost always work on a branch when making changes to my website – this way I can safely test changes before deploying them to my live site. To create a branch:

1. Check that you’re on `main` by typing `git branch` into the RStudio Terminal. If you’re not on `main`, you can switch by running `git checkout main`.

2. Create a local git branch from `main` by running the following in your Terminal:

```{r filename="Command line / Terminal"}
#| eval: false
#| echo: true
git checkout -b my-new-branch
```

3. Push your new local branch to GitHub by running the following in your Terminal:

```{r filename="Command line / Terminal"}
#| eval: false
#| echo: true
git push -u origin my-new-branch
```

You’re now ready to work as normal! Once satisfied with your changes, you can `git add`, `git commit -m "my commit message"`, and `git push` (or use the RStudio GUI buttons in the Git tab) your files. Open a pull request from GitHub and merge into `main` to integrate your changes (this step is important! Your site will not redeploy until your changes have been merged from your branch into `main`).
:::
